---
title: "tidyverse で処理"
output: 
  html_notebook: 
    fig_height: 7
    fig_width: 7
    smart: no
    toc: yes
---

```{r eval=FALSE, include=FALSE}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.


(初回だけ)パッケージのインストール
```{r eval=FALSE, include=FALSE}
#パッケージのインストール
install.packages("tidyverse")

```

パッケージの読み込み
```{r}
#パッケージの読み込み
library("tidyverse")

```

データ読み込み ファイル名指定
```{r}
# データ読み込み ファイル名指定
f <-
  read.table(
    'data-sakata-ymd-10-88-18.csv',
    sep = ",",
    skip = 1,
    header = F,
    fileEncoding = "Shift_JIS",
    stringsAsFactors = F,
    # 空白を削除する
    na.strings=c("", "NULL")
  )
f
```
